Untitled

### 2021-05-11 Main_Figures/Traits_Table.Rmd
prepare table at home

---
title: "Untitled"
output:
  pdf_document: default
  html_document: default

---

@@

library(kableExtra)
library(dplyr)

Trait <- c("Plant height (m)", " ", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovule number/flower",
           "Flowers per plant", "Nectar $(\\mu l)$", "Nectar (mg)", "Nectar concentration (%)", "Pollen grains per flower", "Autonomous selfing (fruit set)")

@@

T.cat <- c("Short-lived, perennial", "Herb, shrub, tree", "Brush, campanulate, capitulum, open, papilionaceous, tube", "Actinomorphic, zygomorphic",
           "Presence/absence", "None, low, medium, high", "Incompatible, partially compatible, compatible", "Hermaphrodite, monoecious, dioecious"," ", " ", " ", " ", " ")

@@

Type_1 <- c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Floral", "Reproductive", "Reproductive","Reproductive","","","","")

@@

colnames(dat) <- c("Trait Type","Traits","Trait Type", "Traits", "Categories")

@@

kable(dat,"latex", longtable = T, booktabs = T,linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = "left") %>% collapse_rows(columns = c(1,3), valign = "middle")

>>>>

---
title: ""
output:
  pdf_document: default
  html_document: default
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
---

@@

library(kableExtra)

library(dplyr)

Trait <- c("Plant height (m)", " ", "Flower width (mm)", "Flower length (mm)", "Inflorescence width (mm)", "Style length (mm)", "Ovule number/flower",
           "Flowers/plant", "Nectar ($\\mu$l)", "Nectar (mg)", "Nectar concentration ($\\%$)", "Pollen grains/flower", "Autonomous selfing (fruit set)")

@@

T.cat <- c("Short-lived, perennial", "Herb, shrub, tree", "Brush, campanulate, capitulum, open, papilionaceous, tube", "Actinomorphic, zygomorphic",
           "Presence/absence", "None, low, medium, high", "Self-incompatible, partially self-compatible, self-compatible", "Hermaphrodite, monoecious, dioecious"," ", " ", " ", " ", " ")

@@

Type_1 <- c("Vegetative", "Vegetative", "Floral", "Floral", "Floral", "Reproductive", "Reproductive", "Reproductive","","","","","")

@@

colnames(dat) <- c("Trait type","Traits","Trait type", "Traits", "Categories")

@@

kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE) %>%
kable_styling(full_width = T) %>%
add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 3),bold=T)  %>%
    column_spec(c(1,3), bold = T) %>% row_spec(0, bold=T)
